Tampering detection for low-power smart cameras

### 2015-05-15 paper.tex
Pushato

\begin{equation}
\label{eq:energyGradient}
g(t) = \mathcal{G}[z_t] =\frac{\sum_{\mathcal{X}}\| \nabla z_t(x) \| _2^2 }{|\mathcal{X}|} ,
\end{equation}

@@

@@

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Configuration}:\\
	\lnl{DEF-Tr0} Extract regions $\{R_k\}, k=1,\dots,K$  \\
	\lnl{DEF-Tr1} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DEF-Tr2} Acquire frame $z_t$ \\
		\lnl{DEF-Tr2a} \For{$k=1,\dots,K$}{
			\lnl{DEF-Tr3a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
		}
		\lnl{DEF-Tr3} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
	}
	\lnl{DEF-Tr6a} \For{$k=1,\dots,K$}{
		\lnl{DEF-Tr7a} Define thresholds $\Gamma_{min}^k$ and $\Gamma_{max}^k$\\
	}
	\lnl{DEF-Tr5} Define CDT parameters on $g(t)$ variance\\
	\textbf{Operational phase}:\\
	\lnl{DEF-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DEF-Test2} Acquire frame $z_t$ \\
		\lnl{DEF-Tr3b} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
		\lnl{DEF-Test2a} $n=0$\\
		\lnl{DEF-Test4a} \For{$k=1,\dots,K$}{
			\lnl{DEF-Test5a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
			\lnl{DEF-Test6a} \If{$\frac{\partial g^k}{\partial t}(t) < \Gamma_{min}^k \vee \frac{\partial g^k}{\partial t}(t) > \Gamma_{max}^k $}{
				\lnl{DEF-Test7a} $n=n+1$\\
			}
		}
		\lnl{DEF-Test81} \If{$n \geq K-1$}{
			\lnl{DEF-Test91} $z_t$ is a defocused frame\\
		}
		\lnl{DEF-Test8} \If{CDT detect a change on $g(t)$ variance}{
			\lnl{DEF-Test9} $z_t$ is a defocused frame\\
		}
	}   
	\caption{Blur detection algorithm}
	\label{alg:DEFOCUS}
\end{algorithm}

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Configuration}:\\
	\lnl{DISPL-Tr1} Extract regions $\{R_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Acquire frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\frac{\partial l^k}{\partial t}(t)$ for the region $R_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Define thresholds $\Gamma_{min}^k$ and $\Gamma_{max}^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Acquire frame $z_t$ \\
		\lnl{DISPL-Test3} $n = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\frac{\partial l^k}{\partial t}(t)$ for the region $R_k$\\
			\lnl{DISPL-Test6} \If{$\frac{\partial l^k}{\partial t}(t) < \Gamma_{min}^k \vee \frac{\partial l^k}{\partial t}(t) > \Gamma_{max}^k $}{
				\lnl{DISPL-Test7} $n=n+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a displaced frame\\
		}
	}   
	\caption{Displacement detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

@@

\begin{figure}
	\centering
	\subfigure[]{\label{fig:ROCdefocus} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus.pdf}}
	\subfigure[]{\label{fig:ROCdefocusZOOM} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocusZOOM.pdf}}
	\subfigure[]{\label{fig:ROCdispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement.pdf}}
	\subfigure[]{\label{fig:ROCdisplZOOM} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacementZOOM.pdf}}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROC}
\end{figure}

>>>>

\begin{equation}
\label{eq:gradientRegions}
\begin{array}{ccc}
g^k(t)&  = & \mathcal{G}^k[z_t] = \frac{\sum_{\mathcal{R}_k}\| \nabla z_t(x) \| _2^2 }{|{\mathcal{R}_k}|}\\
\partial g^k(t) & =& g^k(t)-g^k(t-1) 
\end{array},
\end{equation}

@@

\begin{equation}
\label{eq:lumaRegions}
\begin{array}{ccc}
l^k(t)&  = & \mathcal{L}^k[z_t] = \frac{\sum_{\mathcal{R}_k} z_t(x) }{|{\mathcal{R}_k}|}\\
\partial l^k(t) & =& l^k(t)-l^k(t-1) 
\end{array},
\end{equation}

@@

%\begin{algorithm}[tp]
%	% \SetAlgoNoLine
%	\LinesNumbered
%	\SetAlgoNlRelativeSize{0}
%	\SetNlSty{small}{}{.}
%	\textbf{Configuration}:\\
%	\lnl{DEF-Tr0} Extract regions $\{R_k\}, k=1,\dots,K$  \\
%	\lnl{DEF-Tr1} \For{$t=1,\dots,T_{o}$}
%	{	\lnl{DEF-Tr2} Acquire frame $z_t$ \\
%		\lnl{DEF-Tr2a} \For{$k=1,\dots,K$}{
%			\lnl{DEF-Tr3a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
%		}
%		\lnl{DEF-Tr3} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
%	}
%	\lnl{DEF-Tr6a} \For{$k=1,\dots,K$}{
%		\lnl{DEF-Tr7a} Define thresholds $\Gamma_{min}^k$ and $\Gamma_{max}^k$\\
%	}
%	\lnl{DEF-Tr5} Define CDT parameters on $g(t)$ variance\\
%	\textbf{Operational phase}:\\
%	\lnl{DEF-Test1} \For{$t=T_{o},\dots,\infty$}{
%		\lnl{DEF-Test2} Acquire frame $z_t$ \\
%		\lnl{DEF-Tr3b} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
%		\lnl{DEF-Test2a} $n=0$\\
%		\lnl{DEF-Test4a} \For{$k=1,\dots,K$}{
%			\lnl{DEF-Test5a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
%			\lnl{DEF-Test6a} \If{$\frac{\partial g^k}{\partial t}(t) < \Gamma_{min}^k \vee \frac{\partial g^k}{\partial t}(t) > \Gamma_{max}^k $}{
%				\lnl{DEF-Test7a} $n=n+1$\\
%			}
%		}
%		\lnl{DEF-Test81} \If{$n \geq K-1$}{
%			\lnl{DEF-Test91} $z_t$ is a defocused frame\\
%		}
%		\lnl{DEF-Test8} \If{CDT detect a change on $g(t)$ variance}{
%			\lnl{DEF-Test9} $z_t$ is a defocused frame\\
%		}
%	}   
%	\caption{Blur detection algorithm}
%	\label{alg:DEFOCUS}
%\end{algorithm}

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{\mathcal{R}_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{\mathcal{R}_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $\mathcal{R}_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $\mathcal{R}_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

@@

\begin{figure}
	\centering
	\subfigure[]{\label{fig:ROCdisplZOOM} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacementZOOM.pdf}}
%	\subfigure[]{\label{fig:ROCdefocus} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus.pdf}}
	\subfigure[]{\label{fig:ROCdefocusZOOM} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocusZOOM.pdf}}
%	\subfigure[]{\label{fig:ROCdispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement.pdf}}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROC}
\end{figure}
